Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER. 
This suggests that our model has better speech quality compared with discriminative models but 
worse in speech intelligibility. One possible reason might be related 
to the discretization process on the mixture 
speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
Discretization on the mixed
speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid 
support 
this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech, and it has 
achieved similar dWER with Spex+. Another reason might be related to LM. Right now our encoder-only 
LM satisfies roughly 50\% accuracy. We think using auto-regressive or masking models will achieve 
better results.

>>>>

We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER. 
This suggests that our model has better speech quality compared with discriminative models but 
worse in speech intelligibility. One possible reason might be related 
to the discretization process on the mixture 
speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
 For speech enhancement, this might be 
good because the level of noise will usually be smaller than the speech. Kmeans might achieve the 
effect of denoising. Discretization on the mixed
speech, however, might cause the output to focus on wrong speakers. 
Our results from TSELM-L-Hybrid 
support 
this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech without discretizing, and it has 
achieved similar dWER with Spex+. Another reason might be related to LM. Right now our encoder-only 
LM satisfies roughly 50\% accuracy. We think using auto-regressive or masking models will achieve 
better results.
